Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2016-12-28 Const_design.tex
Presubmission v2

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

An information-theoretic relaying strategy (based on Superposition
Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
The fundamental idea of the SC-approach is to split each data symbol
$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
each of the resulting data streams separately throughout the system
(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
represents a \textquotedbl{}true WNC\textquotedbl{} information stream
(limited by the amount of available HSI) in the system, the superposed
part defines the \textquotedbl{}routed\textquotedbl{} information
which is appended on top of the WNC stream to exploit any potential
spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
for more details). A simplified description of SC-based relaying in
an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
\par\end{centering}
\caption{Relaying scheme for the uncoded WBN
system. DEM stands for a hard decision demodulator, IC is the interference
canceler.\label{fig:CTUpp_Information-flow-uncoded-block-scheme}}
\end{figure*}
\begin{table}
\centering{}%
\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
\hline 
\textbf{Step 1: Source transmission}
\begin{itemize}
\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
\begin{equation}
s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
\end{equation}

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}\includegraphics[width=0.8\textwidth]{fig/d2_1}\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/const_all_2}
\par\end{centering}

@@

In addition to the analytical evaluation of throughput, we validate
the results in a real-world setup. The hardware performance is evaluated
using Ettus Research Universal Software Radio Peripherals (USRPs)
which are computer-hosted Software Defined Radios (SDRs). The USRPs
connect to a host computer via a Gigabit Ethernet link, which the
host-based software uses to receive and transmit the baseband IQ stream.
The host controls the USRP using USRP Hardware Driver (UHD) commands,
including setting parameters such as amplifier gain. The USRP then
performs the necessary baseband processing then up/down-conversion
and transmission/reception. The Ettus Research N210 USRP is used,
which consists of a motherboard and a Radio Frequency (RF) daughterboard;
more details can be found in \cite{Ettus_flyer}. In these experiments
the XCVR2450 daughterboards are used, these are dual-band transceivers
with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
tool-kit, is used as the host-processing software.
\begin{figure}
\centering{}\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}\caption{Setup for HW evaluation (Ettus Research
USRPs). Source transmissions are prerotated \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
to imitate the AWGN channel conditions (as used in the numerical evaluation).
To allow a strict control of HSI channels SNR in the HW
setup, the HSI channels are emulated by adding a Gaussian noise to
the respective source signal and the resulting emulated HSI is passed
to destinations via UDP. This also avoids the problem of node visibility
where direct links $S_{A}\rightarrow D_{A}$ and $S_{B}\rightarrow D_{B}$
exist in the laboratory environment.\label{fig:CTUpp_HW_setup}}
\end{figure}

@@

\begin{itemize}
\item The constellations with ($N_{b}=0,\,N_{s}>0$) assume full multi-user
detection at the relay and hence they do not exploit the HSI channels
(Table~\ref{tab:CTUpp_SC-relaying-scheme}). Consequently, their
throughput does not depend on $\gamma_{{\rm {HSI}}}$. However, their
performance worsens with decreasing $\gamma_{{\rm {MAC}}}$ (compare
Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput16_20})
and deteriorates quite dramatically with decreasing $\gamma_{{\rm {BC}}}$
(compare Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The constellations with ($N_{b}>0,\,N_{s}=0$) require a reliable
HSI channel and hence their throughput is zero for low $\gamma_{{\rm {HSI}}}$
and grows up to $N_{b}$ for high $\gamma_{{\rm {HSI}}}$ and sufficiently
high $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$ (all Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The performance of all constellations with ($N_{b}>0,\,N_{s}>0$)
is influenced by all system SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
Remarkably, for some particular values of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$
these constellations significantly outperform those with $N_{b}=0$
or $N_{s}=0$ in the medium $\gamma_{{\rm {HSI}}}$ region (Figs.~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_16}).
Note that this is a direct consequence of superior $\rho_{\mathrm{HSI}}^{2}$
performance of these constellations\footnote{It can be shown that for constant $N_{b}+N_{s}$ the minimum Euclidean
distance $\rho_{\mathrm{HSI}}^{2}$ grows with decreasing $N_{b}$,
resulting in a more efficient utilization of \textquotedbl{}imperfect\textquotedbl{}
HSI channels \cite{Uricar-Sykora_2012,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
and consequently in a more reliable overheard HSI for the constellations
with lower (non-zero) $N_{b}$.} for constant $N_{b}+N_{s}$, i.e. for constant bits/constellation
symbol transmitted by the sources.
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=16\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput16_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=17\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=17\,\mathrm{dB}$
and given $(N_{b},N_{s})$.\label{fig:CTUpp_Throughput17_17}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=20\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput20_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
\par\end{centering}

@@

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomenas can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}\quad\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
\par\end{centering}

\centering{}\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC20}\quad\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC25}\caption{Throughput performance $T_{\mathrm{LB}}$ and SNR mapping regions
(including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
for $\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$.\label{fig:CTUpp_SNR_map_BC15-17-20-25}}
\end{figure*}
\begin{figure*}
\centering{}\includegraphics[width=0.48\textwidth]{fig/XOR_map_Througput_BC20}\quad\includegraphics[width=0.48\textwidth]{fig/XOR_map_Througput_USRP_BC20}\caption{Comparison of $T_{\mathrm{LB}}$ and the throughput performance evaluated
in a real world adaptive HW setup ($T_{\mathrm{USRP}}$) for $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$.
The SNR mapping regions (including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
used in the HW evaluation are also emphasized in the figure.\label{fig:CTUpp_SNR_map_BC20_USRP}}
\vspace*{-4ex}
\end{figure*}

@@

After decoding all required data streams ($\mathbf{\hat{D}}_{A}^{s},\,\hat{\mathbf{D}}_{B}^{s},\,\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$),
the relay creates a joint data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
and re-encodes it as $\mathcal{C}_{R}(\mathbf{D}_{R})=\mathbf{C}_{R}=[\mathbf{c}_{R,0},\mathbf{c}_{R,1},\dots,\mathbf{c}_{R,\mathcal{N}-1}]$.
The encoded data are then mapped to the output $2^{N_{R}}$-QAM (where
$N_{R}=2N_{s}+N_{b}$) constellation symbols $s_{R,j}=\mathcal{A}^{R}\left(\mathbf{c}_{r,j}\right)$,
$j\in\{0,1,\dots,\mathcal{N}-1\}$ and broadcast by the relay to both
destination nodes.
\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
\par\end{centering}

@@

\bibliographystyle{bmc_template/bmc-mathphys}
\bibliography{bib/bib,bib/uricar,bib/uricar-papers,bib/uricar-books,bib/sykora,bib/books}

>>>>

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.
\begin{figure}
\centering{}
\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

@@

An information-theoretic relaying strategy (based on Superposition
Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
The fundamental idea of the SC-approach is to split each data symbol
$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
each of the resulting data streams separately throughout the system
(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
represents a \textquotedbl{}true WNC\textquotedbl{} information stream
(limited by the amount of available HSI) in the system, the superposed
part defines the \textquotedbl{}routed\textquotedbl{} information
which is appended on top of the WNC stream to exploit any potential
spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
for more details). A simplified description of SC-based relaying in
an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
\par\end{centering}
\caption{Relaying scheme for the uncoded WBN
system. DEM stands for a hard decision demodulator, IC is the interference
canceler.\label{fig:CTUpp_Information-flow-uncoded-block-scheme}}
\end{figure*}
\begin{table}
\centering{}%
\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
\hline 
\textbf{Step 1: Source transmission}
\begin{itemize}
\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
\begin{equation}
s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
\end{equation}

@@

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).
\begin{figure*}
\centering{}
\includegraphics[width=0.8\textwidth]{fig/d2_1}
\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/const_all_2}
\par\end{centering}

@@

In addition to the analytical evaluation of throughput, we validate
the results in a real-world setup. The hardware performance is evaluated
using Ettus Research Universal Software Radio Peripherals (USRPs)
which are computer-hosted Software Defined Radios (SDRs). The USRPs
connect to a host computer via a Gigabit Ethernet link, which the
host-based software uses to receive and transmit the baseband IQ stream.
The host controls the USRP using USRP Hardware Driver (UHD) commands,
including setting parameters such as amplifier gain. The USRP then
performs the necessary baseband processing then up/down-conversion
and transmission/reception. The Ettus Research N210 USRP is used,
which consists of a motherboard and a Radio Frequency (RF) daughterboard;
more details can be found in \cite{Ettus_flyer}. In these experiments
the XCVR2450 daughterboards are used, these are dual-band transceivers
with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
tool-kit, is used as the host-processing software.
\begin{figure}
\centering{}
\includegraphics[width=0.95\columnwidth]{fig/20150109_143009}
\caption{Setup for HW evaluation (Ettus Research
USRPs). Source transmissions are prerotated \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008}
to imitate the AWGN channel conditions (as used in the numerical evaluation).
To allow a strict control of HSI channels SNR in the HW
setup, the HSI channels are emulated by adding a Gaussian noise to
the respective source signal and the resulting emulated HSI is passed
to destinations via UDP. This also avoids the problem of node visibility
where direct links $S_{A}\rightarrow D_{A}$ and $S_{B}\rightarrow D_{B}$
exist in the laboratory environment.\label{fig:CTUpp_HW_setup}}
\end{figure}

@@

\begin{itemize}
\item The constellations with ($N_{b}=0,\,N_{s}>0$) assume full multi-user
detection at the relay and hence they do not exploit the HSI channels
(Table~\ref{tab:CTUpp_SC-relaying-scheme}). Consequently, their
throughput does not depend on $\gamma_{{\rm {HSI}}}$. However, their
performance worsens with decreasing $\gamma_{{\rm {MAC}}}$ (compare
Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput16_20})
and deteriorates quite dramatically with decreasing $\gamma_{{\rm {BC}}}$
(compare Figs.~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The constellations with ($N_{b}>0,\,N_{s}=0$) require a reliable
HSI channel and hence their throughput is zero for low $\gamma_{{\rm {HSI}}}$
and grows up to $N_{b}$ for high $\gamma_{{\rm {HSI}}}$ and sufficiently
high $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$ (all Figs.~\ref{fig:CTUpp_Throughput16_20},~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_20},~\ref{fig:CTUpp_Throughput20_16}).
\item The performance of all constellations with ($N_{b}>0,\,N_{s}>0$)
is influenced by all system SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}},\,\gamma_{{\rm {HSI}}}$).
Remarkably, for some particular values of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$
these constellations significantly outperform those with $N_{b}=0$
or $N_{s}=0$ in the medium $\gamma_{{\rm {HSI}}}$ region (Figs.~\ref{fig:CTUpp_Throughput17_17},~\ref{fig:CTUpp_Throughput20_16}).
Note that this is a direct consequence of superior $\rho_{\mathrm{HSI}}^{2}$
performance of these constellations\footnote{It can be shown that for constant $N_{b}+N_{s}$ the minimum Euclidean
distance $\rho_{\mathrm{HSI}}^{2}$ grows with decreasing $N_{b}$,
resulting in a more efficient utilization of \textquotedbl{}imperfect\textquotedbl{}
HSI channels \cite{Uricar-Sykora_2012,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
and consequently in a more reliable overheard HSI for the constellations
with lower (non-zero) $N_{b}$.} for constant $N_{b}+N_{s}$, i.e. for constant bits/constellation
symbol transmitted by the sources.
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC16_BC20_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=16\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput16_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC17_BC17_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=17\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=17\,\mathrm{dB}$
and given $(N_{b},N_{s})$.\label{fig:CTUpp_Throughput17_17}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC20_N2}
\par\end{centering}

\caption{Comparison of throughput as a function of $\gamma_{{\rm {HSI}}}$
for $\gamma_{{\rm {MAC}}}=20\,\mathrm{dB},\,\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$
and given $(N_{b},N_{s})$. \label{fig:CTUpp_Throughput20_20}}
\end{figure}
\begin{figure}
\begin{centering}
\hspace*{-0.04\columnwidth}
\includegraphics[clip,width=0.95\columnwidth]{fig/Throughput_HSI_XOR_MAC20_BC16_N2}
\par\end{centering}

@@

The SNR mapping regions, including the resulting throughput for the
optimal choice of $N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$, are shown
as a function of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$ for
$\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$
in Fig.~\ref{fig:CTUpp_SNR_map_BC15-17-20-25}. Several interesting
phenomenas can be again observed in the figure:
\begin{itemize}
\item Since the transmission schemes with ($N_{b}=0,\,N_{s}>0$) constellations
can ignore the HSI channels (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
these constellations are optimal in the low $\gamma_{{\rm {HSI}}}$
region ($\gamma_{{\rm {HSI}}}<8\,\mathrm{dB}$), regardless of the
other channels' SNRs $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The constellations with ($N_{b}>0,\,N_{s}=0$) provide the best performance
in a substantial part of the medium-to-high $\gamma_{{\rm {HSI}}}$
regions, depending on the actual $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {BC}}}$.
\item The \textquotedbl{}combined\textquotedbl{} constellations ($N_{b}>0,\,N_{s}>0$)
provide the maximal throughput (for sufficiently high $\gamma_{{\rm {BC}}}$)
in relatively large regions of $\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}}$
(see the dominant throughput regions of $(N_{b}^{{\rm I}},\,N_{s}^{{\rm I}})=(2,1)$
for $\gamma_{{\rm {BC}}}=\left\{ 20\,\mathrm{dB},\,25\,\mathrm{dB}\right\} $).
Note that these constellations have a great potential for application
in systems with limited or partial HSI (see \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}).
\begin{figure*}
\begin{centering}
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC15}
\quad
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC17}
\par\end{centering}

\centering{}
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC20}
\quad
\includegraphics[width=0.45\textwidth]{fig/XOR_map_Througput_BC25}
\caption{Throughput performance $T_{\mathrm{LB}}$ and SNR mapping regions
(including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
for $\gamma_{{\rm {BC}}}\in\{15\,\mathrm{dB},\,17\,\mathrm{dB},20\,\mathrm{dB},25\,\mathrm{dB}\}$.\label{fig:CTUpp_SNR_map_BC15-17-20-25}}
\end{figure*}
\begin{figure*}
\centering{}
\includegraphics[width=0.45\linewidth]{fig/XOR_map_Througput_BC20}
\,
\includegraphics[width=0.45\linewidth]{fig/XOR_map_Througput_USRP_BC20}
\caption{Comparison of $T_{\mathrm{LB}}$ and the throughput performance evaluated
in a real world adaptive HW setup ($T_{\mathrm{USRP}}$) for $\gamma_{{\rm {BC}}}=20\,\mathrm{dB}$.
The SNR mapping regions (including the optimal const. parameters ($N_{b}^{{\rm I}},\,N_{s}^{{\rm I}}$))
used in the HW evaluation are also emphasized in the figure.\label{fig:CTUpp_SNR_map_BC20_USRP}}
\vspace*{-4ex}
\end{figure*}

@@

After decoding all required data streams ($\mathbf{\hat{D}}_{A}^{s},\,\hat{\mathbf{D}}_{B}^{s},\,\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})$),
the relay creates a joint data word $\mathbf{D}_{R}=[\mathbf{\hat{D}}_{A}^{s},\hat{\mathbf{D}}_{B}^{s},\hat{f}(\mathbf{D}_{A}^{b},\mathbf{D}_{B}^{b})]$
and re-encodes it as $\mathcal{C}_{R}(\mathbf{D}_{R})=\mathbf{C}_{R}=[\mathbf{c}_{R,0},\mathbf{c}_{R,1},\dots,\mathbf{c}_{R,\mathcal{N}-1}]$.
The encoded data are then mapped to the output $2^{N_{R}}$-QAM (where
$N_{R}=2N_{s}+N_{b}$) constellation symbols $s_{R,j}=\mathcal{A}^{R}\left(\mathbf{c}_{r,j}\right)$,
$j\in\{0,1,\dots,\mathcal{N}-1\}$ and broadcast by the relay to both
destination nodes.
\begin{figure*}
\begin{centering}
\includegraphics[width=0.95\textwidth]{fig/butterfly-2level_processing_principleTWC-coded}
\par\end{centering}

@@

\bibliographystyle{bmc_template/bmc-mathphys}
\bibliography{bib/Const_design}
